\documentclass[letterpaper,12pt]{extarticle}
\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

\setpdftargetpages

\begin{document}
\vspace{-4.0\baselineskip}
\hourheading{August 8 -- Holy Father Dominic}
%\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen, Alleluia.}

\prayerheading{Examination of Conscience}
\begin{verse}
	\side{All} I confess to almighty God, \\*
	to blessed Mary ever virgin, \\*
	to blessed Dominic our father, \\*
	to all the saints, and to you, bretheren, \\*
	that I have sinned exceedingly \\*
	by thought, word, deed, and omission, through my fault: \\*
	I beseech you to pray for me.

	\side{Leader} May almighty God have mercy on us \\*
	and forgive us all our sins, \\*
	may he free us from all evil, \\*
	keep us safe and strengthen us in every good work, \\*
	and bring us to eternal life.

	\side{All} Amen.
\end{verse}

\prayerheading{HYMN}
\begin{verse}
	1. Dominic, our Lady's champion, \\*
Charged to publish wide her fame, \\*
Sent to men to sound her Ave \\*
And to speak her glorious name; \\*
With the grace of God within you, \\*
Like a hero lord you came.

2. Stainless as a burnished chalice, \\*
Shining as a fiery brand, \\*
Dominic, you came to help us, \\*
Came to do your Lord's command, \\*
With the grace of God within you \\*
And the rosary in your hand.

3. Now again we need your goodness: \\*
Be our patron and our guide. \\*
Save us from all sin and error, \\*
From our blindness and our pride; \\*
With the grace of God within us, \\*
May we stand close by your side.

\end{verse}
%\prayerheading{PSALMODY}
%\newpage
\psalmheading{Psalm 91}
\vspace{-1.5\baselineskip}
\antiphon{Leader 1}{Night holds no terrors for me sleeping under God's wings.}
\vspace{-1.0\baselineskip}
\begin{verse} \setlength{\stanzaskip}{0.25\baselineskip}
\side{Leader 1} He who dwells in the shelter of the Most High \\*
\side{Side 1} and abides in the shade of the Almighty \\*
says to the Lord: “My refuge,  \\*
my stronghold, my God in whom I trust!”

\side{Side 2} It is he who will free you from the snare  \\*
of the fowler who seeks to destroy you; \\*
he will conceal you with his pinions  \\*
and under his wings you will find refuge.

\side{Side 1} You will not fear the terror of the night  \\*
nor the arrow that flies by day, \\*
nor the plague that prowls in the darkness  \\*
nor the scourge that lays waste at noon.

\side{Side 2} A thousand may fall at your side,  \\*
ten thousand fall at your right, \\*
you, it will never approach;  \\*
his faithfulness is buckler and shield.

\side{Side 1} Your eyes have only to look  \\*
to see how the wicked are repaid, \\*
you who have said: “Lord, my refuge!”  \\*
and have made the Most High your dwelling.

\side{Side 2} Upon you no evil shall fall,  \\*
no plague approach where you dwell. \\*
For you has he commanded his angels,  \\*
to keep you in all your ways.

\side{Side 1} They shall bear you upon their hands  \\*
lest you strike your foot against a stone. \\*
On the lion and the viper you will tread  \\*
and trample the young lion and the dragon.

\side{Side 2} Since he clings to me in love, I will free him;  \\*
protect him for he knows my name. \\*
When he calls I shall answer: “I am with you,”  \\*
I will save him in distress and give him glory.

\side{Side 1} With length of life I will content him;  \\*
I shall let him see my saving power. \\*

\side{Side 2} Glory to the Father, and to the Son,  \\*
and to the Holy Spirit: \\*
\side{Side 1} as it was in the beginning, is now,  \\*
and will be for ever. Amen.

\end{verse}
\antiphon{All}{Night holds no terrors for me sleeping under God's wings.}
%\newpage

\psalmheading{\textbf{READING}\\Revelation 22:4-5}
%\begin{quote}
\sidestar{Reader}\\*
They shall see the Lord face to face and bear his name on their foreheads. The
night shall be no more. They will need no light from lamps or the sun, for the
Lord God shall give them light, and they shall reign forever.
%\end{quote}
%\newpage
\prayerheading{RESPONSORY}
\sidestar{Reader} Into your hands, Lord, I commend my spirit. \\
%\rednote{---} 
\sidestar{All} Into your hands, Lord, I commend my spirit.

\sidestar{Reader} You have redeemed us, Lord God of truth. \\
%\rednote{---}
\sidestar{All} I commend my spirit.

\sidestar{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
%\rednote{---} 
\sidestar{All} Into your hands, Lord, I commend my spirit.

\psalmheading{\textbf{CANTICLE OF SIMEON}\\ Luke 2:29-32}
%\rednote{All stand}
\vspace{-1.5\baselineskip}
\antiphon{Leader}{Protect us, Lord, as we stay awake; watch over us as we sleep,
that awake, we may keep watch with christ, and asleep, rest in his peace.}
\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
	\side{All} Lord, \rednote{+} now you let your servant go in peace; \\*
your word has been fulfilled:

my own eyes have seen the salvation \\*
which you have prepared in the sight of every people:

a light to reveal you to the nations \\*
and the glory of your people Israel.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{Protect us, Lord, as we stay awake; watch over us as we sleep,
that awake, we may keep watch with christ, and asleep, rest in his peace.}

\prayerheading{PRAYER}
\vspace{-1.5\baselineskip}
\sidestar{Leader}\\*
Lord, we beg you to visit this house \\*
and banish from it all the deadly power of the enemy. \\*
May your holy angels dwell here to keep us in peace; \\*
and may your blessing be upon us always. \\*
We ask this through Christ our Lord. \\*
\sidestar{All} Amen.

%\prayerheading{Antiphon to the Blessed Virgin}
%Salve Regina
%
%\prayerheading{Antiphon to Holy Father Dominic}
%O Lumen

\end{document}
