\documentclass[letterpaper,14pt]{extarticle}
\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

\setpdftargetpages

\begin{document}
\hourheading{Twentieth Sunday of Ordinary Time}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen, Alleluia.}

\prayerheading{HYMN}
\begin{verse}
	Love divine, all loves excelling, \\*
	Joy of heaven, to earth come down, \\*
And impart to us, here dwelling, \\*
Grace and mercy all around. \\*
Jesus, source of all compassion, \\*
Pure, unbounded love you share; \\*
Grant us many choicest blessings, \\*
Keep us in your loving care.

Come, O source of inspiration, \\*
Pure and spotless let us be: \\*
Let us see your true salvation, \\*
Perfect in accord with thee. \\*
Praising Father for all glory \\*
With the Spirit and the Son; \\*
Everlasting thanks we give thee, \\*
Undivided, love, in one.

\end{verse}
%\prayerheading{PSALMODY}
%\newpage
\psalmheading{Psalm 110:1-5,7}
\antiphon{Leader 1}{In eternal splendor, before the dawn of light on earth,
I have begotten you, alleluia.}  
\begin{verse}
\side{Leader 1} The Lord’s revelation to my Master: \\*
\side{Side 1} ``Sit on my right: \\*
your foes I will put beneath your feet.''

\side{Side 2} The Lord will wield from Zion \\*
your scepter of power: \\*
rule in the midst of all your foes.

\side{Side 1} A prince from the day of your birth \\*
on the holy mountains; \\*
from the womb before the dawn I begot you.

\side{Side 2} The Lord has sworn an oath he will not change. \\*
“You are a priest for ever, \\*
a priest like Melchizedek of old.”

\side{Side 1} The Master standing at your right hand \\*
will shatter kings in the day of his great wrath.

\side{Side 2} He shall drink from the stream by the wayside \\*
and therefore he shall lift up his head. 

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{In eternal splendor, before the dawn of light on earth,
I have begotten you, alleluia.}  
%\newpage
\psalmheading{Psalm 112}
\antiphon{Leader 2}{Blessed are they who hunger and thirst for holiness; they
will be satisfied.}
\begin{verse}

\side{Leader 2} Happy the man who fears the Lord, \\*
\side{Side 2} who takes delight in all his commands. \\*
His sons will be powerful on earth;  \\*
the children of the upright are blessed.

\side{Side 1} Riches and wealth are in his house;  \\*
his justice stands firm for ever. \\*
He is a light in the darkness for the upright:  \\*
he is generous, merciful and just.

\side{Side 2} The good man takes pity and lends,  \\*
he conducts his affairs with honor. \\*
The just man will never waver:  \\*
he will be remembered for ever.

\side{Side 1} He has no fear of evil news;  \\*
with a firm heart he trusts in the Lord. \\*
With a steadfast heart he will not fear;  \\*
he will see the downfall of his foes.

\side{Side 2} Open-handed, he gives to the poor;  \\*
his justice stands firm for ever.  \\*
His head will be raised in glory.

\side{Side 1} The wicked man sees and is angry,  \\*
grinds his teeth and fades away;  \\*
the desire of the wicked leads to doom.

\side{Side 2} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 1}as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{Blessed are they who hunger and thirst for holiness; they will
be satisfied.}

\psalmheading{Revelation 19:1-7}
\antiphon{Leader 1}{Praise God, all you who serve him, both great and small,
alleluia.}
\setlength{\stanzaskip}{0.25\baselineskip}
\vspace{-1.5\baselineskip}
\begin{verse}
\side{Leader 1} Alleluia. \\*
\side{Side 1} Salvation, glory, and power to our God: \\*
his judgments are honest and true. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
Sing praise to our God, all you his servants, \\*
all who worship him reverently, great and small. \\*
Alleluia.

\side{Side 1} Alleluia. \\ *
The Lord our all-powerful God is King; \\*
Let us rejoice, sing praise, and give him glory. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
The wedding feast of the Lamb has begun, \\*
and his bride is prepared to welcome him. \\*
Alleluia.

\side{Side 1} Alleluia. \\*
Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
Alleluia.

\side{Side 2} Alleluia. \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen. \\*
Alleluia 
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{Praise God, all you who serve him, both great and small,
alleluia.}

\psalmheading{\textbf{READING}\\Hebrews 12:22-24}
%\begin{quote}
\sidestar{Reader}\\*
You have drawn near to Mount Zion and the city of the living God, the heavenly
Jerusalem, to myriads of angels in festal gathering, to the assembly of the
first-born enrolled in heaven, to God the judge of all, to the spirits of just
men made perfect, to Jesus, the mediator of a new covenant, and to the
sprinkled blood which speaks more eloquently than that of Abel.
%\end{quote}
%\newpage
\prayerheading{RESPONSORY}
\sidestar{Reader} Our Lord is great, mighty is his power. \\
%\rednote{---} 
\sidestar{All} Our Lord is great, mighty is his power.

\sidestar{Reader} His wisdom is beyond compare, \\
%\rednote{---}
\sidestar{All} mighty is his power

\sidestar{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
%\rednote{---} 
\sidestar{All} Our Lord is great, mighty is his power.

\psalmheading{\textbf{CANTICLE OF MARY}\\ Luke 1:49-55}
\rednote{All stand}
\antiphon{Leader}{I have come to cast fire upon the earth; how I long to see
the flame leap up!}
\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} My \rednote{+} soul proclaims the greatness of the Lord, \\*
my spirit rejoices in God my Savior \\*
for he has looked with favor on his lowly servant.

From this day all generations will call me blessed: \\*
the Almighty has done great things for me, \\*
and holy is his Name.

He has mercy on those who fear him \\*
in every generation.

He has shown the strength of his arm, \\*
he has scattered the proud in their conceit.

He has cast down the mighty from their thrones, \\*
and has lifted up the lowly.

He has filled the hungry with good things, \\*
and the rich he has sent away empty.

He has come to the help of his servant Israel \\*
for he has remembered his promise of mercy, \\*
the promise he made to our fathers, \\*
to Abraham and his children for ever.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{I have come to cast fire upon the earth; how I long to see
the flame leap up!}

\prayerheading{INTERCESSIONS}
\intercession{Rejoicing in the Lord, from whom all good things come, let us pray:}
{\textit{Lord, hear our prayer.}}

\intercession{Father and Lord of all, you sent your Son into the world, that your name might be glorified in every place,}
{strengthen the witness of your Church among the nations.}

\intercession{Make us obedient to the teachings of your apostles,}
{and bound to the truth of our faith.}

\intercession{As you love the innocent,}
{render justice to those who are wronged.}

\intercession{Free those in bondage and give sight to the blind,}
{raise up the fallen and protect the stranger.}

\intercession{Fulfill your promise to those who already sleep in your peace,}
{through your Son grant them a blessed resurrection.}

\prayerheading{THE LORD'S PRAYER}
\antiphon{Leader}{Gathering our prayer and praises into one, let us offer the
prayer Christ himself taught us:}
\begin{verse}
	\side{All} Our Father, who art in heaven, [...] \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\prayerheading{CONCLUDING PRAYER}
\sidestar{Leader}\\*

O God, you have prepared for those who love you \\*
good things which no eye can see, \\*
fill our hearts, we pray, with the warmth of your love, \\*
so that, loving you in all things and above all things, \\*
we may attain your promises, \\*
which surpass every human desire. \\*
Through our Lord Jesus Christ, your Son, \\*
who lives and reigns with you in the unity of the Holy Spirit, \\*
one God, for ever and ever. \\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{Leader}\\*
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.
\end{document}
