\documentclass[letterpaper,14pt]{extarticle}
\usepackage[fontsize=19pt]{scrextend}
\usepackage[left=0.7in,right=0.3in,top=0.1in,bottom=0.5in]{geometry}
%\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

%\setpdftargetpages

\begin{document}
\hourheading{Memorial of St. Catherine de Ricci}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen.}

%\prayerheading{PSALMODY}
\psalmheading{Psalm 92}
\antiphon{Leader 1}{I live, no longer I, but Christ lives in me; I bear the marks of Jesus on my body.}
\begin{verse}
\side{Leader 1} It is good to give thanks to the Lord,  \\*
\side{Side 1} to make music to your name, O Most High, \\*
to proclaim your love in the morning  \\*
and your truth in the watches of the night, \\*
on the ten-stringed lyre and the lute,  \\*
with the murmuring sound of the harp.

\side{Side 2} Your deeds, O Lord, have made me glad;  \\*
for the work of your hands I shout with joy. \\*
O Lord, how great are your works!  \\*
How deep are your designs! \\*
The foolish man cannot know this  \\*
and the fool cannot understand.

\side{Side 1} Though the wicked spring up like grass  \\*
and all who do evil thrive: \\*
they are doomed to be eternally destroyed.  \\*
But you, Lord, are eternally on high. \\*
See how your enemies perish;  \\*
all doers of evil are scattered.

\side{Side 2} To me you give the wild-ox's strength;  \\*
you anoint me with the purest oil. \\*
My eyes looked in triumph on my foes;  \\*
my ears heard gladly of their fall. \\*
The just will flourish like the palm-tree  \\*
and grow like a Lebanon cedar.

\side{Side 1} Planted in the house of the Lord,  \\*
they will flourish in the courts of our God, \\*
still bearing fruit when they are old,  \\*
still full of sap, still green, \\*
to proclaim that the Lord is just.  \\*
In him, my rock, there is no wrong \\*

\side{Side 2} Glory to the Father, and to the Son,  \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now,  \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{I live, no longer I, but Christ lives in me; I bear the marks of Jesus on my body.}

\psalmheading{Ezekiel 36:24-28}
\antiphon{Leader 2}{I will create a new heart in you, and breathe into you a new spirit.}
\begin{verse}
\side{Leader 2} I will take you away from among the nations, \\*
\side{Side 2} gather you from all the foreign lands, \\*
and bring you back to your own land.

\side{Side 1} I will sprinkle clean water upon you \\*
to cleanse you from all your impurities, \\*
and from all your idols I will cleanse you.

\side{Side 2} I will give you a new heart \\*
and place a new spirit within you, \\*
taking from your bodies your stony hearts \\*
and giving you natural hearts.

\side{Side 1} I will put my spirit within you \\*
and make you live by my statutes, \\*
careful to observe my decrees.

\side{Side 2} You shall live in the land I gave your fathers; \\*
you shall be my people, \\*
and I will be your God.

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{I will create a new heart in you, and breathe into you a new spirit.}

\psalmheading{Psalm 8}
\antiphon{Leader 1}{Clothe yourself in everlasting glory, and you will see the splendor of God.}
%\setlength{\stanzaskip}{0.25\baselineskip}
%\vspace{-1.5\baselineskip}
\begin{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\side{Leader 1} How great is your name, O Lord our God, \\*
\side{Side 1} through all the earth!

\side{Side 2} Your majesty is praised above the heavens; \\*
on the lips of children and of babes \\*
you have found praise to foil your enemy, \\*
to silence the foe and the rebel.

\side{Side 1} When I see the heavens, the work of your hands, \\*
the moon and the stars which you arranged, \\*
what is man that you should keep him in mind, \\*
mortal man that you care for him?

\side{Side 2} Yet you have made him little less than a god; \\*
with glory and honor you crowned him, \\*
gave him power over the works of your hands, \\*
put all things under his feet.

\side{Side 1} All of them, sheep and cattle, \\*
yes, even the savage beasts, \\*
birds of the air, and fish \\*
that make their way through the waters.

\side{Side 2} How great is your name, O Lord our God \\*
through all the earth!

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{Clothe yourself in everlasting glory, and you will see the splendor of God.}


\psalmheading{\textbf{READING}\\2 Cor 4:8,10-11a}
\rednote{Reader:} We are afflicted in every way, but not constrained; perplexed, but not driven to despair; always carrying about in the body the dying of Jesus, so that the life of Jesus may also be manifested in our body.  For we who live are constantly being given up to death for the sake of Jesus.
%\newpage
\prayerheading{RESPONSORY}
\begin{verse}
\side{Reader} My heart is ever pleading, show me your face. \\
\side{All} My heart is ever pleading, show me your face.

\side{Reader} I long to gaze upon you God, \\
\side{All} Show me your face.

\side{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
\side{All} My heart is ever pleading, show me your face.
\end{verse}

\psalmheading{\textbf{Reflection}}
\psalmheading{\textbf{CANTICLE OF ZECHARIAH}\\ Luke 1:68-79}
\rednote{All stand}
\antiphon{Leader}{Arise, hasten and come, O virgin Catherine, for you have washed your robes white in the blood of the Lamb.  You were faithful to death; accept from the Lord the crown of life.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} Blessed \rednote{+} be the Lord, the God of Israel; \\*
he has come to his people and set them free.

He has raised up for us a mighty savior, \\*
born of the house of his servant David.

Through his holy prophets he promised of old \\*
  that he would save us from our enemies, \\*
  from the hands of all who hate us.

He promised to show mercy to our fathers \\*
and to remember his holy covenant.

This was the oath he swore to our father Abraham: \\*
to set us free from the hands of our enemies, \\*
free to worship him without fear, \\*
holy and righteous in his sight \\*
   all the days of our life.

You, my child, shall be called the prophet of the Most High; \\*
for you will go before the Lord to prepare his way, \\*
to give his people knowledge of salvation \\*
by the forgiveness of their sins.

In the tender compassion of our God \\*
the dawn from on high shall break upon us, \\*
to shine on those who dwell in darkness and the shadow of death, \\*
and to guide our feet into the way of peace.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{Arise, hasten and come, O virgin Catherine, for you have washed your robes white in the blood of the Lamb.  You were faithful to death; accept from the Lord the crown of life.}

\prayerheading{INTERCESSIONS}
\intercession{Christ is the spouse and the crowning glory of virgins.  Let us praise him with joy in our voices and pray to him with sincerity in our hearts:}
{\textit{Jesus, crown of virgins, hear us.}}

\intercession{Christ, the holy virgins loved you as their one true spouse,}
{grant that nothing may separate us from your love.}

\intercession{You crowned Mary, your mother, queen of virgins,}
{through her intercession, let us continually serve you with pure hearts.}

\intercession{Your handmaids were always careful to love you with whole and undivided attention, that they might be holy in body and spirit,}
{through their intercession grant that the lure of this passing world may not distract our attention from you.}

\intercession{Lord Jesus, you are the spouse whose coming was anticipated by the wise virgins,}
{grant that we may wait for you in hope and expectation.}

\intercession{Through the intercession of Saint Catherine, who was one of the wise and prudent virgins,}
{grant us wisdom and innocence of life.}

\prayerheading{THE LORD'S PRAYER}
\antiphon{Leader}{Remember us, Lord, when you come to your kingdom and teach us how to pray:}
	
\begin{verse}
	\side{All} Our Father, who art in heaven,\\ %[$\cdots$] \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\psalmheading{CONCLUSION}

\sidestar{President}\\*
O God, who made the virgin Saint Catherine \\*
outstanding for the contemplation of the Passion of your Son, \\*
grant us, through her intercession, \\*
that, reflecting devoutly on these same mysteries, \\*
we may come to attain their reward. \\*
Through our Lord Jesus Christ, your Son,\\*
who lives and reigns with you in the unity of the Holy Spirit,\\*
God, for ever and ever.\\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{President}
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.

\sidestar{President}
May the souls of the faithful departed,  \\*
through the mercy of God, rest in peace. \\*
\sidestar{All} Amen.

\end{document}
