\documentclass[letterpaper,14pt]{extarticle}
\usepackage[fontsize=19pt]{scrextend}
\usepackage[left=0.7in,right=0.3in,top=0.1in,bottom=0.5in]{geometry}
%\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

%\setpdftargetpages

\begin{document}
\hourheading{January 19, 2020: Second Sunday of Ordinary Time}
\prayerheading{Agenda}

\begin{itemize}
	\item 2:00 Refreshments and Community Building
	\begin{itemize}
		\item Prayer Partner Exchange
	\end{itemize}
	\item 2:20 Study --- Decree on the Apostolate of the Laity \\ (\textit{Apostolicam Actuositatem}) \\ 
	Rule for Lay Fraternities with provincial guidelines paragraphs 1-7

\item 3:05 Business
	\begin{itemize}
		\item Reflection --- Marie
		\item Approval of Previous Minutes
		\item Dues
		\item 2020 Sign ups (refreshments and reflections)
		\item Feast of St Thomas Aquinas?
		\item Other concerns or announcements
	\end{itemize}
	\item 3:35 --- Evening prayer
	\item Next meeting: February 16
	\item Next study topic: St. Dominic
\end{itemize}
\subsubsection*{Upcoming Dominican Feasts}
January 23: Blessed Henry Suso (Not on the calendar)\\
January 28: St. Thomas Aquinas (Feast)\\
February 4: St. Catherine de Ricci (Optional Memorial)\\
February 7: Commemoration of Deceased Parents\\
February 12: Blessed Reginald of Orl\'{e}ans (Not on the calendar)\\
February 13: Blessed Jordan of Saxony (Memorial)
\pagebreak
\hourheading{Evening Prayer}
\prayerheading{HYMN: number 84, page 1599, (vs. 2\&3)}
\prayerheading{PSALMODY AND READING: Week 2, page 786}

\psalmheading{\textbf{CANTICLE OF MARY}\\ Luke 1:49-55}
\rednote{All stand}
\antiphon{Leader}{There was a wedding in Cana of Galilee, and Jesus was there with Mary his mother.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} My \rednote{+} soul proclaims the greatness of the Lord, \\*
my spirit rejoices in God my Savior \\*
for he has looked with favor on his lowly servant.

From this day all generations will call me blessed: \\*
the Almighty has done great things for me, \\*
and holy is his Name.

He has mercy on those who fear him \\*
in every generation.

He has shown the strength of his arm, \\*
he has scattered the proud in their conceit.

He has cast down the mighty from their thrones, \\*
and has lifted up the lowly.

He has filled the hungry with good things, \\*
and the rich he has sent away empty.

He has come to the help of his servant Israel \\*
for he has remembered his promise of mercy, \\*
the promise he made to our fathers, \\*
to Abraham and his children for ever.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{There was a wedding in Cana of Galilee, and Jesus was there with Mary his mother.}

\prayerheading{INTERCESSIONS}
\intercession{All praise and honor to Christ! He lives for ever to intercede for us, and he is able to save those who approach the Father in his name. Sustained by our faith, let us call upon him:}
{\textit{Remember your people, Lord.}}

\intercession{As the day draws to a close, Sun of Justice, we invoke your name upon the whole human race,}
{so that all men may enjoy your never failing light.}

\intercession{Preserve the covenant which you have ratified in your blood,}
{cleanse and sanctify your Church.}

\intercession{Unite all Christians in worship and in faith,}
{Make them one as you and the Father are one.}

\intercession{Remember your assembly, Lord,}
{your dwelling place.}

\intercession{Guide travelers along the path of peace and prosperity,}
{so that they may reach their destinations in safety and joy.}

\intercession{Receive the souls of those who have died O Lord, especially those of the Dominican order,}
{grant them your favor and the gift of eternal glory.}

\prayerheading{THE LORD'S PRAYER}
	
\psalmheading{CONCLUSION}

\sidestar{Leader}\\*
Almighty ever-living God,\\*
who govern all things,\\*
both in heaven and on earth,\\*
mercifully hear the pleading of your people\\*
and bestow your peace on our times.\\*
Through our Lord Jesus Christ, your Son,\\*
who lives and reigns with you in the unity of the Holy Spirit,\\*
one God, for ever and ever.\\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{Leader}\\*
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.
\end{document}
