\documentclass[letterpaper,14pt]{extarticle}
\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

\setpdftargetpages

\begin{document}
\hourheading{The Most Holy Body and Blood of Christ}
%\prayerheading{INTRODUCTION}
\vspace{-0.5\baselineskip}
\hspace{\leftmargini}\rednote{(Begin Standing; Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen, Alleluia.}
\vspace{-1.0\baselineskip}

\prayerheading{HYMN}
\vspace{-1.5\baselineskip}
\begin{verse}
	Tantum ergo Sacramentum \\
	Veneremur cernui: \\
	Et antiquum documentum \\
	Novo cedat ritui: \\
	Praestet fides supplementum \\
	Sensuum defectui. 

	 Genitori, Genitoque \\
	Laus et iubilatio, \\
	Salus, honor, virtus quoque \\
	Sit et benedictio: \\
	Procedenti ab utroque \\
	Compar sit laudatio.  Amen. 
\end{verse}
%\prayerheading{PSALMODY}
%\newpage
\vspace{-0.5\baselineskip}
\rednote{(All sit for Psalmody)}
\vspace{-1.875\baselineskip}
\psalmheading{Psalm 110:1-5,7}
\vspace{-1.5\baselineskip}
\antiphon{Leader 1}{Christ the Lord is a priest for ever in the line of
Melchizedek; he offered up bread and wine.}  
\vspace{-1.0\baselineskip}
\begin{verse}
\side{Leader 1} The Lord’s revelation to my Master: \\*
\side{Side 1} ``Sit on my right: \\*
your foes I will put beneath your feet.''

\side{Side 2} The Lord will wield from Zion \\*
your scepter of power: \\*
rule in the midst of all your foes.

\side{Side 1} A prince from the day of your birth \\*
on the holy mountains; \\*
from the womb before the dawn I begot you.

\side{Side 2} The Lord has sworn an oath he will not change. \\*
“You are a priest for ever, \\*
a priest like Melchizedek of old.”

\side{Side 1} The Master standing at your right hand \\*
will shatter kings in the day of his great wrath.

\side{Side 2} He shall drink from the stream by the wayside \\*
and therefore he shall lift up his head. 

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{Christ the Lord is a priest for ever in the line of
Melchizedek; he offered up bread and wine.}  
%\newpage
\psalmheading{Psalm 116:10-19}

\antiphon{Leader 2}{I will take up the cup of salvation, and I will offer a
sacrifice of praise.}
\begin{verse}
\side{Leader 2} I trusted, even when I said: \\
\side{Side 2} “I am sorely afflicted,” \\
and when I said in my alarm: \\
“There is no one I can trust.”

\side{Side 1}How can I repay the Lord \\
for his goodness to me? \\
The cup of salvation I will raise; \\
I will call on the Lord’s name.

\side{Side 2} My vows to the Lord I will fulfill \\
before all his people. \\
O precious in the eyes of the Lord \\
is the death of his faithful.

\side{Side 1} Your servant, Lord, your servant am I; \\
you have loosened my bonds. \\
A thanksgiving sacrifice I make; \\
I will call on the Lord’s name.

\side{Side 2} My vows to the Lord I will fulfill \\
before all his people, \\
in the courts of the house of the Lord, \\
in your midst, O Jerusalem.

\side{Side 1} Glory to the Father, and to the Son, \\
and to the Holy Spirit:\\
\side{Side 2} as it was in the beginning, is now, \\
and will be for ever. Amen
\end{verse}
\antiphon{All}{I will take up the cup of salvation, and I will offer a
sacrifice of praise.}

\psalmheading{Revelation 19:1-7}
\antiphon{Leader 1}{You are the way, the truth and the life of the world, 
O Lord.}
\setlength{\stanzaskip}{0.25\baselineskip}
\vspace{-1.5\baselineskip}
\begin{verse}
\side{Leader 1} Alleluia. \\*
\side{Side 1} Salvation, glory, and power to our God: \\*
his judgments are honest and true. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
Sing praise to our God, all you his servants, \\*
all who worship him reverently, great and small. \\*
Alleluia.

\side{Side 1} Alleluia. \\ *
The Lord our all-powerful God is King; \\*
Let us rejoice, sing praise, and give him glory. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
The wedding feast of the Lamb has begun, \\*
and his bride is prepared to welcome him. \\*
Alleluia.

\side{Side 1} Alleluia. \\*
Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
Alleluia.

\side{Side 2} Alleluia. \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen. \\*
Alleluia 
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{You are the way, the truth and the life of the world, 
O Lord.}

\psalmheading{\textbf{READING}\\1 Corinthians 11:23-24}
%\begin{quote}
\sidestar{Reader}\\*
I received from the Lord what I handed on to you, namely, that the Lord Jesus
on the night in which he was betrayed took bread, and after he had given
thanks, broke it and said, “This is my body, which is for you. Do this in
remembrance of me.” In the same way, after the supper, he took the cup,
saying, “This cup is the new covenant in my blood. Do this, whenever you drink
it, in remembrance of me.”
%\end{quote}
%\newpage
\prayerheading{RESPONSORY}
\sidestar{Reader} He gave them bread from heaven, alleluia, alleluia. \\
%\rednote{---} 
\sidestar{All} He gave them bread from heaven, alleluia, alleluia. \\

\sidestar{Reader} Man has eaten the bread of angels, \\
%\rednote{---}
\sidestar{All} alleluia, alleluia.

\sidestar{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
%\rednote{---} 
\sidestar{All} He gave them bread from heaven, alleluia, alleluia.

\psalmheading{\textbf{CANTICLE OF MARY}\\ Luke 1:49-55}
\rednote{All stand}
\antiphon{Leader}{How holy this feast in which Christ is our food; his passion
is recalled; grace fills our hearts; and we receive a pledge of the glory to
come, alleluia.}
\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} My \rednote{+} soul proclaims the greatness of the Lord, \\*
my spirit rejoices in God my Savior \\*
for he has looked with favor on his lowly servant.

From this day all generations will call me blessed: \\*
the Almighty has done great things for me, \\*
and holy is his Name.

He has mercy on those who fear him \\*
in every generation.

He has shown the strength of his arm, \\*
he has scattered the proud in their conceit.

He has cast down the mighty from their thrones, \\*
and has lifted up the lowly.

He has filled the hungry with good things, \\*
and the rich he has sent away empty.

He has come to the help of his servant Israel \\*
for he has remembered his promise of mercy, \\*
the promise he made to our fathers, \\*
to Abraham and his children for ever.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{How holy this feast in which Christ is our food; his passion
is recalled; grace fills our hearts; and we receive a pledge of the glory to
come, alleluia.}

\prayerheading{INTERCESSIONS}

\intercession{Christ invites all to the supper in which he gives his body and
blood for the life of the world. Let us ask him:}
{\textit{Christ, the bread of heaven, grant us everlasting life.}}

\intercession{Christ, Son of the living God, you commanded that this
thanksgiving meal be done in memory of you,}
{enrich your Church through the faithful celebration of these mysteries.}

\intercession{Christ, eternal priest of the Most High, you have commanded your
priests to offer your sacraments,}
{may they help them to exemplify in their lives the meaning of the sacred
mysteries which they celebrate.}

\intercession{Christ, bread from heaven, you form one body out of all who
partake of the one bread,}
{refresh all who believe in you with harmony and peace.}

\intercession{Christ, through your bread you offer the remedy for immortality
and the pledge of future resurrection,}
{restore health to the sick and living hope to sinners.}

\intercession{Christ, our king who is to come, you commanded the mysteries
which proclaim your death to be celebrated until you return,}
{grant that all who die in you may share in your resurrection.}

\prayerheading{THE LORD'S PRAYER}
\antiphon{Leader}{Gathering our prayer and praises into one, let us offer the
prayer Christ himself taught us:}
\begin{verse}
	\side{All} Our Father, who art in heaven, [...] %\\
%hallowed be thy name; \\
%thy kingdom come; \\
%thy will be done on earth \\
%as it is in heaven. \\
%Give us this day our daily bread; \\
%and forgive us our trespasses \\
%as we forgive those who trespass against us; \\
%and lead us not into temptation, \\
%but deliver us from evil.
\end{verse}

\prayerheading{CONCLUDING PRAYER}
\sidestar{Leader}\\*
O God, who in this wonderful Sacrament \\
have left us a memorial of your Passion, \\
grant us, we pray, \\ 
so to revere the sacred mysteries of your Body and Blood \\
that we may always experience in ourselves \\
the fruits of your redemption. \\
Who live and reign with God the Father \\
in the unity of the Holy Spirit, \\
one God, for ever and ever. \\
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{Leader}\\*
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.
\end{document}
