\documentclass[letterpaper,14pt]{extarticle}
\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{5em}

\newcommand{\antiphon}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{#1} & \textbf{#2}
	\end{tabular}}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}

\setpdftargetpages

\begin{document}
\hourheading{Fifth Sunday of Easter}
\prayerheading{INTRODUCTION}
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen, Alleluia.}

\prayerheading{HYMN}
\begin{verse}
At the Lamb's high feast we sing \\*
praise to our victorious King, \\*
who has washed us in the tide \\*
flowing from his pierced side; \\*
praise we him whose love divine \\*
gives his sacred blood for wine, \\*
gives his body for the feast, \\*
Christ the victim, Christ the priest.

Where the paschal blood is poured, \\*
death's dark angel sheathes his sword; \\*
Israel's hosts triumphant go \\*
through the wave that drowns the foe. \\*
Praise we Christ, whose blood was shed, \\*
paschal victim, paschal bread; \\*
with sincerity and love \\*
eat we manna from above.
\end{verse}
\prayerheading{PSALMODY}
%\newpage
\psalmheading{Psalm 110:1-5,7}
\antiphon{Leader 1}{The Lord is risen and is seated at the right hand of God,
alleluia.}  
\begin{verse}
\side{Leader 1} The Lord’s revelation to my Master: \\*
\side{Side 1} ``Sit on my right: \\*
your foes I will put beneath your feet.''

\side{Side 2} The Lord will wield from Zion \\*
your scepter of power: \\*
rule in the midst of all your foes.

\side{Side 1} A prince from the day of your birth \\*
on the holy mountains; \\*
from the womb before the dawn I begot you.

\side{Side 2} The Lord has sworn an oath he will not change. \\*
“You are a priest for ever, \\*
a priest like Melchizedek of old.”

\side{Side 1} The Master standing at your right hand \\*
will shatter kings in the day of his great wrath.

\side{Side 2} He shall drink from the stream by the wayside \\*
and therefore he shall lift up his head. 

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{The Lord is risen and is seated at the right hand of God,
alleluia.}
%\newpage
\psalmheading{Psalm 114}
\antiphon{Leader 2}{He has rescued us from the power of darkness and has brought
us into the kingdom of his Son, alleluia.}
\begin{verse}
\side{Leader 2} When Israel came forth from Egypt,  \\*
\side{Side 2} Jacob’s sons from an alien people, \\*
Judah became the Lord’s temple,  \\*
Israel became his kingdom.

\side{Side 1} The sea fled at the sight:  \\*
the Jordan turned back on its course, \\*
the mountains leapt like rams  \\*
and the hills like yearling sheep.

\side{Side 2} Why was it, sea, that you fled, \\*
that you turned back, Jordan, on your course? \\*
Mountains, that you leapt like rams, \\*
hills, like yearling sheep?

\side{Side 1} Tremble, O earth, before the Lord, \\*
in the presence of the God of Jacob, \\*
who turns the rock into a pool \\*
and flint into a spring of water.

\side{Side 2} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 1}as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{He has rescued us from the power of darkness and has brought
us into the kingdom of his Son, alleluia.}

\psalmheading{Revelation 19:1-7}
\antiphon{Leader 1}{Alleluia, our God is king; glory and praise to him,
alleluia.}
\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\side{Leader 1} Alleluia. \\*
\side{Side 1} Salvation, glory, and power to our God: \\*
his judgments are honest and true. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
Sing praise to our God, all you his servants, \\*
all who worship him reverently, great and small. \\*
Alleluia.

\side{Side 1} Alleluia. \\ *
The Lord our all-powerful God is King; \\*
Let us rejoice, sing praise, and give him glory. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
The wedding feast of the Lamb has begun, \\*
and his bride is prepared to welcome him. \\*
Alleluia.

\side{Side 1} Alleluia. \\*
Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
Alleluia.

\side{Side 2} Alleluia. \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen. \\*
Alleluia 
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{Alleluia, our God is king; glory and praise to him, alleluia.}

\psalmheading{\textbf{READING}\\Hebrews 10:12-14}
%\begin{quote}
\sidestar{Reader}\\*
Jesus offered one sacrifice for sins and took his seat forever at the right
hand of God; now he waits until his enemies are placed beneath his feet. By
one offering he has forever perfected those who are being sanctified.
%\end{quote}
%\newpage
\prayerheading{RESPONSORY}
\sidestar{Reader} The Lord is risen, alleluia, alleluia. \\
%\rednote{---} 
\sidestar{All} The Lord is risen, alleluia, alleluia.

\sidestar{Reader} He has appeared to Simon, \\
%\rednote{---}
\sidestar{All} alleluia, alleluia.

\sidestar{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
%\rednote{---} 
\sidestar{All} The Lord is risen, alleluia, alleluia.

\psalmheading{\textbf{CANTICLE OF MARY}\\ Luke 1:49-55}
\antiphon{Leader}{I give you a new commandment: love one another as I have loved
you, says the Lord, alleluia.}
\begin{verse}
\side{All} My \rednote{+} soul proclaims the greatness of the Lord, \\*
my spirit rejoices in God my Savior \\*
for he has looked with favor on his lowly servant.

From this day all generations will call me blessed: \\*
the Almighty has done great things for me, \\*
and holy is his Name.

He has mercy on those who fear him \\*
in every generation.

He has shown the strength of his arm, \\*
he has scattered the proud in their conceit.

He has cast down the mighty from their thrones, \\*
and has lifted up the lowly.

He has filled the hungry with good things, \\*
and the rich he has sent away empty.

He has come to the help of his servant Israel \\*
for he has remembered his promise of mercy, \\*
the promise he made to our fathers, \\*
to Abraham and his children for ever.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{I give you a new commandment: love one another as I have loved
you, says the Lord, alleluia.}

\prayerheading{INTERCESSIONS}
\antiphon{Leader}{With joy in our hearts, let us call upon Christ the Lord, who
died and rose again, and lives always to intercede for us:}\\*
\begin{centering} \sidestar{All} \textit{Victorious King, hear our prayer.}\end{centering}

\intercession{Light and salvation of all peoples, send into our hearts the fire of your Spirit}{as we proclaim your resurrection.}

\intercession{Let Israel recognize in you her longed-for Messiah}
{and the whole earth be filled with the knowledge of your glory.}

\intercession{Keep us in the communion of your saints,}
{and grant us rest from our labors in their company.}

\intercession{You have triumphed over death, your enemy; destroy in us the
power of death,}
{that we may live only for you, victorious and immortal Lord.}

\intercession{Savior Christ, you were obedient even to accepting death, and
were raised up to the right hand of the Father,}
{in your goodness welcome your brothers and sisters into the
kingdom of your glory.}

\prayerheading{THE LORD'S PRAYER}
\antiphon{Leader}{Gathering our prayer and praises into one, let us offer the
prayer Christ himself taught us:}

\sidestar{All}\\
Our Father, who art in heaven, \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.

\prayerheading{CONCLUDING PRAYER}
\sidestar{Leader}\\*
Almighty ever-living God, \\*
constantly accomplish the Paschal Mystery within us, \\*
that those you were pleased to make new in Holy Baptism \\*
may, under your protective care, bear much fruit \\*
and come to the joys of life eternal. \\*
Through our Lord Jesus Christ, your Son, \\*
who lives and reigns with you in the unity of the Holy Spirit, \\*
one God, for ever and ever. \\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{Leader}\\*
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.
\end{document}
