\documentclass[letterpaper,14pt]{extarticle}
\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

\setpdftargetpages

\begin{document}
\hourheading{Twenty Ninth Sunday in Ordinary Time}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen, Alleluia.}

\prayerheading{HYMN}
\begin{verse}
Faith of our Fathers! living still \\*
In spite of dungeon, fire, and sword: \\*
Oh, how our hearts beat high with joy \\*
Whene'er we hear that glorious word.

Faith of our Fathers! Holy Faith! \\*
We will be true to thee till death.

Faith of our Fathers! we will love \\*
Both friend and foe in all our strife: \\*
And preach thee too, as love knows how\\*
By kindly words and virtuous life:

Faith of our Fathers! Holy Faith!\\*
We will be true to thee till death.

\end{verse}
%\prayerheading{PSALMODY}
%\newpage
\psalmheading{Psalm 110:1-5,7}
\antiphon{Leader 1}{The Lord will stretch forth his mighty scepter from Zion, and he will reign for ever,
alleluia.}  
\begin{verse}
\side{Leader 1} The Lord’s revelation to my Master: \\*
\side{Side 1} ``Sit on my right: \\*
your foes I will put beneath your feet.''

\side{Side 2} The Lord will wield from Zion \\*
your scepter of power: \\*
rule in the midst of all your foes.

\side{Side 1} A prince from the day of your birth \\*
on the holy mountains; \\*
from the womb before the dawn I begot you.

\side{Side 2} The Lord has sworn an oath he will not change. \\*
“You are a priest for ever, \\*
a priest like Melchizedek of old.”

\side{Side 1} The Master standing at your right hand \\*
will shatter kings in the day of his great wrath.

\side{Side 2} He shall drink from the stream by the wayside \\*
and therefore he shall lift up his head. 

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{The Lord will stretch forth his mighty scepter from Zion, and he will reign for ever,
alleluia.}
%\newpage
\psalmheading{Psalm 114}
\antiphon{Leader 2}{The earth is shaken to its depths before the glory of your face.}
\begin{verse}
\side{Leader 2} When Israel came forth from Egypt,  \\*
\side{Side 2} Jacob’s sons from an alien people, \\*
Judah became the Lord’s temple,  \\*
Israel became his kingdom.

\side{Side 1} The sea fled at the sight:  \\*
the Jordan turned back on its course, \\*
the mountains leapt like rams  \\*
and the hills like yearling sheep.

\side{Side 2} Why was it, sea, that you fled, \\*
that you turned back, Jordan, on your course? \\*
Mountains, that you leapt like rams, \\*
hills, like yearling sheep?

\side{Side 1} Tremble, O earth, before the Lord, \\*
in the presence of the God of Jacob, \\*
who turns the rock into a pool \\*
and flint into a spring of water.

\side{Side 2} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 1}as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{The earth is shaken to its depths before the glory of your face.}

\psalmheading{Revelation 19:1-7}
\antiphon{Leader 1}{All power is yours, Lord God, our mighty King, alleluia.}
\setlength{\stanzaskip}{0.25\baselineskip}
\vspace{-1.5\baselineskip}
\begin{verse}
\side{Leader 1} Alleluia. \\*
\side{Side 1} Salvation, glory, and power to our God: \\*
his judgments are honest and true. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
Sing praise to our God, all you his servants, \\*
all who worship him reverently, great and small. \\*
Alleluia.

\side{Side 1} Alleluia. \\ *
The Lord our all-powerful God is King; \\*
Let us rejoice, sing praise, and give him glory. \\*
Alleluia.

\side{Side 2} Alleluia. \\*
The wedding feast of the Lamb has begun, \\*
and his bride is prepared to welcome him. \\*
Alleluia.

\side{Side 1} Alleluia. \\*
Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
Alleluia.

\side{Side 2} Alleluia. \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen. \\*
Alleluia 
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{All power is yours, Lord God, our mighty King, alleluia.}


\psalmheading{\textbf{READING}\\2 Corinthians 1:3-4}
%\begin{quote}
\sidestar{Reader}\\*
Praised be God, the Father of our Lord Jesus Christ, the Father of mercies and
the God of all consolation! He comforts us in all our afflictions and thus
enables us to comfort those who are in trouble, with the same consolation we
have received from him.

%\end{quote}
%\newpage
\prayerheading{RESPONSORY}
\sidestar{Reader}The whole creation proclaims the greatness of your glory.\\
%\rednote{---} 
\sidestar{All} The whole creation proclaims the greatness of your glory.

\sidestar{Reader} Eternal ages praise\\
%\rednote{---}
\sidestar{All} the greatness of your glory.

\sidestar{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
%\rednote{---} 
\sidestar{All} The whole creation proclaims the greatness of your glory.

\psalmheading{\textbf{CANTICLE OF MARY}\\ Luke 1:49-55}
\rednote{All stand}
\antiphon{Leader}{When the Son of Man comes to earth, do you think he will find faith in men’s hearts?}
\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} My \rednote{+} soul proclaims the greatness of the Lord, \\*
my spirit rejoices in God my Savior \\*
for he has looked with favor on his lowly servant.

From this day all generations will call me blessed: \\*
the Almighty has done great things for me, \\*
and holy is his Name.

He has mercy on those who fear him \\*
in every generation.

He has shown the strength of his arm, \\*
he has scattered the proud in their conceit.

He has cast down the mighty from their thrones, \\*
and has lifted up the lowly.

He has filled the hungry with good things, \\*
and the rich he has sent away empty.

He has come to the help of his servant Israel \\*
for he has remembered his promise of mercy, \\*
the promise he made to our fathers, \\*
to Abraham and his children for ever.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{When the Son of Man comes to earth, do you think he will find faith in men’s hearts?}

\prayerheading{INTERCESSIONS}
\intercession{Christ the Lord is our head; we are his members. In joy let us call out to him:}
{\textit{Lord, may your kingdom come.}}

\intercession{Christ our Savior, make your Church a more vivid symbol of the unity of all mankind,}
{make it more effectively the sacrament of salvation for all peoples.}

\intercession{Through your presence, guide the college of bishops in union with the Pope,}
{give them the gifts of unity, love and peace.}

\intercession{Bind all Christians more closely to yourself, their divine Head,}
{lead them to proclaim your kingdom by the witness of their lives.}

\intercession{Grant peace to the world,}
{let every land flourish in justice and security.}

\intercession{Grant to the dead the glory of resurrection,}
{and give us a share in their happiness.}

\prayerheading{THE LORD'S PRAYER}
\antiphon{Leader}{Gathering our prayer and praises into one, let us offer the
prayer Christ himself taught us:}
\begin{verse}
\side{All} Our Father, who art in heaven, \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\prayerheading{CONCLUDING PRAYER}
\sidestar{Leader}\\*
Almighty ever-living God, \\*
grant that we may always conform our will to yours\\*
and serve your majesty in sincerity of heart\\*
Through our Lord Jesus Christ, your Son, \\*
who lives and reigns with you in the unity of the Holy Spirit, \\*
one God, for ever and ever. \\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{Leader}\\*
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.
\end{document}
