\documentclass[letterpaper,14pt]{extarticle}
\usepackage[fontsize=17pt]{scrextend}
\usepackage[left=0.7in,right=0.3in,top=0.1in,bottom=0.5in]{geometry}
%\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

%\setpdftargetpages

\begin{document}
\include{offices/saturday_II_morning}
\renewcommand{\antiphonone}{She is the brilliance of eternal light an a mirror without defect.}
\renewcommand{\antiphontwo}{Shining dawn of salvation, from you, Virgin Mary, came the Sun of justice who has visited us from on high.}
\renewcommand{\antiphonthree}{Virgin Mother of God, when you stand before the Lord, remember to ask for our good, alleluia.}
\hourheading{Saturday Memorial of Our Lady (Queen of Apostles), Week II}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen. Alleluia.}

%\prayerheading{PSALMODY}
\psalmheading{\psalmoneheading}
\antiphon{Leader 1}{\antiphonone}
\begin{verse}
\input{psalms/psalm92.tex}
\end{verse}
\antiphon{All}{\antiphonone}

\psalmheading{\psalmtwoheading}
\antiphon{Leader 2}{\antiphontwo}
\begin{verse}
\input{psalms/deuteronomy32_1-12.tex}
\end{verse}
\antiphon{All}{\antiphontwo}

\psalmheading{\psalmthreeheading}
\antiphon{Leader 1}{\antiphonthree}
\begin{verse}
\input{psalms/psalm8.tex}
\end{verse}
\antiphon{All}{\antiphonthree}

\psalmheading{\textbf{READING}\\Acts 1:11b, 12, 13a, 14}
\rednote{Reader:} After Jesus was taken into heaven, they returned to Jerusalem from the mount called Olivet, which is near Jerusalem, a sabbath day's journey away.  When they entered the city they went to the upper room where they were staying.  All these devoted themselves with one accord to prayer, together with some women, and Mary the mother of Jesus, and his brothers.
%\newpage
\psalmheading{\textbf{Reflection}}
\prayerheading{RESPONSORY}
\begin{verse}
\side{Reader} God chose her before she was born. \\
\side{All} God chose her before she was born.

\side{Reader} She was made to dwell with God \\
\side{All} before she was born

\side{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
\side{All} God chose her before she was born.
\end{verse}

\psalmheading{\textbf{CANTICLE OF ZECHARIAH}\\ Luke 1:68-79}
\rednote{All stand}
\antiphon{Leader}{The holy Mother of God became beautiful and delightful because of her virginity.  The daughters of Zion who saw her proclaimed her the most beautiful of all the roses and the lilies of the valley; the queens of the earth praised her.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} Blessed \rednote{+} be the Lord, the God of Israel; \\*
he has come to his people and set them free.

He has raised up for us a mighty savior, \\*
born of the house of his servant David.

Through his holy prophets he promised of old \\*
  that he would save us from our enemies, \\*
  from the hands of all who hate us.

He promised to show mercy to our fathers \\*
and to remember his holy covenant.

This was the oath he swore to our father Abraham: \\*
to set us free from the hands of our enemies, \\*
free to worship him without fear, \\*
holy and righteous in his sight \\*
   all the days of our life.

You, my child, shall be called the prophet of the Most High; \\*
for you will go before the Lord to prepare his way, \\*
to give his people knowledge of salvation \\*
by the forgiveness of their sins.

In the tender compassion of our God \\*
the dawn from on high shall break upon us, \\*
to shine on those who dwell in darkness and the shadow of death, \\*
and to guide our feet into the way of peace.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{The holy Mother of God became beautiful and delightful because of her virginity.  The daughters of Zion who saw her proclaimed her the most beautiful of all the roses and the lilies of the valley; the queens of the earth praised her.}

\prayerheading{INTERCESSIONS}
\intercession{With confidence we turn to Mary, Mother of God and Mother of the Church, the Queen of Apostles, and ask her to intercede for us. With her we pray to the Lord, saying:}
{\textit{Help us to open our hearts to your word.}}

\intercession{Lord, you assumed human flesh through the Virgin Mary;}
{purify our hearts that we may receive you.}

\intercession{You gave Mary your mother to the Church;}
{sanctify us with your Holy Spirit tht we may become your servants.}

\intercession{By your death on the cross you brought the mystery of salvation to perfection;}
{through your resurrection lead us into glory.}

\intercession{Your Church praises you, the Lord Almighty,}
{because you died and now you live forever.}

\intercession{Pour out your blessings on our brothers of the Province of the Philippines and
the whole Dominican Family in the Philippines, Sri Lanka and Indonesia.}{Make
them faithful in preaching your Word and bless our Order with new vocations.}

\prayerheading{THE LORD'S PRAYER}
%\antiphon{Leader}{Gathering our prayer and praises into one, let us offer the prayer Christ himself taught us:}
	
\begin{verse}
	\side{All} Our Father, who art in heaven,\\ %[$\cdots$] \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\psalmheading{CONCLUSION}

\sidestar{President}\\*
O God, you wish everyone to be saved and come to a knowledge of the truth. \\*
Make your harvest bountiful and send many harvesters \\*
that the Gospel may be preached to every creature \\*
May your people, gathered bt the word of life \\*
and sustained by the power of the sacraments, \\*
proceed on the way of salvation and charity. \\*
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,\\*
God, for ever and ever.\\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{President}
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.

\sidestar{President}
May the souls of the faithful departed,  \\*
through the mercy of God, rest in peace. \\*
\sidestar{All} Amen.

\end{document}
