\documentclass[letterpaper,14pt]{extarticle}
\usepackage[fontsize=18pt]{scrextend}
\usepackage[left=0.7in,right=0.3in,top=0.1in,bottom=0.5in]{geometry}
%\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

%\setpdftargetpages

\begin{document}
\include{offices/sunday_I_morning}
\renewcommand{\antiphonone}{The angel Gabriel brought God's message to Mary, and she concieved by the power of the Holy Spirit.}
\renewcommand{\antiphontwo}{Mary entered the house of Zechariah, and greeted Elizabeth.}
\renewcommand{\antiphonthree}{She gave birth to her firstborn son, and laid him in a manger.}
\hourheading{Feast of Our Lady of the Rosary}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen.}

%\prayerheading{PSALMODY}
\psalmheading{\psalmoneheading}
\antiphon{Leader 1}{\antiphonone}
\begin{verse}
\input{psalms/psalm63.tex}
\end{verse}
\antiphon{All}{\antiphonone}

\psalmheading{\psalmtwoheading}
\antiphon{Leader 2}{\antiphontwo}
\begin{verse}
\input{psalms/daniel3_57-86.tex}
\end{verse}
\antiphon{All}{\antiphontwo}

\psalmheading{\psalmthreeheading}
\antiphon{Leader 1}{\antiphonthree}
\begin{verse}
\input{psalms/psalm149.tex}
\end{verse}
\antiphon{All}{\antiphonthree}

\psalmheading{\textbf{READING}\\Gal 4:4-5}
\rednote{Reader:} But when the fullness of time had come, God sent his Son, born of a woman, born under the law, to ransom those under the law, so that we might receive adoption.
%\newpage
\prayerheading{RESPONSORY}
\begin{verse}
\side{Reader} The Word became flesh \\
and made his dwelling among us. \\
\side{All} The Word became flesh
and made his dwelling among us. 

\side{Reader} He was in the beginning with God. \\
\side{All} and made his dwelling among us. 

\side{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
\side{All} The Word became flesh
and made his dwelling among us. 
\end{verse}

\psalmheading{\textbf{Reflection}}
\psalmheading{\textbf{CANTICLE OF ZECHARIAH}\\ Luke 1:68-79}
\rednote{All stand}
\antiphon{Leader}{Blessed Mother and inviolate virgin, glorious Queen of the world, may all who celebrate your festival of the most holy Rosary know your protection.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} Blessed \rednote{+} be the Lord, the God of Israel; \\*
he has come to his people and set them free.

He has raised up for us a mighty savior, \\*
born of the house of his servant David.

Through his holy prophets he promised of old \\*
  that he would save us from our enemies, \\*
  from the hands of all who hate us.

He promised to show mercy to our fathers \\*
and to remember his holy covenant.

This was the oath he swore to our father Abraham: \\*
to set us free from the hands of our enemies, \\*
free to worship him without fear, \\*
holy and righteous in his sight \\*
   all the days of our life.

You, my child, shall be called the prophet of the Most High; \\*
for you will go before the Lord to prepare his way, \\*
to give his people knowledge of salvation \\*
by the forgiveness of their sins.

In the tender compassion of our God \\*
the dawn from on high shall break upon us, \\*
to shine on those who dwell in darkness and the shadow of death, \\*
and to guide our feet into the way of peace.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{Blessed Mother and inviolate virgin, glorious Queen of the world, may all who celebrate your festival of the most holy Rosary know your protection.}

\prayerheading{INTERCESSIONS}
\intercession{Trusting in the Virgin who is full of grace and Mother of our Savior we make our prayers to God.}
{\textit{Lord, hear our prayer.}}

\intercession{You chose Mary to become the mother of Christ our Savior;}
{may our desires and actions be according to your will.}

\intercession{With great rejoicing, Mary glorified you;}
{teach us to give thanks for the gifts you have given us.}

\intercession{By the power of the Holy Spirit Mary brought forth your Son;}
{may we give birth to your Word in our world.}

\intercession{The Virgin Mary presented the Redeemer of the World in the temple;}
{may the redeemed of every nation come to the temple of your glory.}

\intercession{After three days, she found her Son who had been lost;}
{may all the departed be gathered in the eternal dwelling of heaven.}

\prayerheading{THE LORD'S PRAYER}
%\antiphon{Leader}{Gathering our prayer and praises into one, let us offer the prayer Christ himself taught us:}
	
\begin{verse}
	\side{All} Our Father, who art in heaven,\\ %[$\cdots$] \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\psalmheading{CONCLUSION}

\sidestar{President}\\*

Pour forth, we beseech you, O Lord, \\*
your grace into our hearts, \\*
that we, to whom the Incarnation of Christ your Son \\*
was made known by the message of an Angel, \\*
may, by his Passion and Cross, \\*
be brought to the glory of his Resurrection. \\*
Who lives and reigns with you in the unity of the Holy Spirit,\\*
God, for ever and ever.\\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{President}
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.

\sidestar{President}
May the souls of the faithful departed,  \\*
through the mercy of God, rest in peace. \\*
\sidestar{All} Amen.

\end{document}
