\documentclass{article}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
\usepackage{booklet}

\begin{document}
\hourheading{Fifth Sunday of Easter}
\instruct{INTRODUCTION}
God, \instruct{+} come to my assistance
\instruct{---} Lord, make haste to help me.

Glory to the Father, and to the Son and to the Holy Spirit:
\instruct{---} as it was in the beginning, is now, and will be for ever. Amen, Alleluia.

\instruct{Ant. 1} The Lord is risen and is seated at the right hand of God, alleluia.  
\psalmheading{Psalm 110:1-5,7}
\lessontitle{The Messiah, king and priest}
\textit{Christ’s reign will last until all his enemies are made subject to him}
(1 Corinthians 15:25).

%\begingroup
%\setlength\parskip{0pt}
%\obeylines
\begin{alltt}\normalfont
The Lord’s revelation to my Master: †
“Sit on my right: *
your foes I will put beneath your feet.”

The Lord will wield from Zion †
your scepter of power: *
rule in the midst of all your foes.

A prince from the day of your birth †
on the holy mountains; *
from the womb before the dawn I begot you.

The Lord has sworn an oath he will not change. †
“You are a priest for ever, *
a priest like Melchizedek of old.”

The Master standing at your right hand *
will shatter kings in the day of his great wrath.

He shall drink from the stream by the wayside *
and therefore he shall lift up his head.

Glory to the Father, and to the Son, *
and to the Holy Spirit:
as it was in the beginning, is now, *
and will be for ever. Amen.
\end{alltt}
%\endgroup
\instruct{Psalm Prayer}

Father, we ask you to give us victory and peace. In Jesus Christ, our Lord and King, we are already seated at your right hand. We look forward to praising you in the fellowship of all your saints in our heavenly homeland.

\instruct{Ant.} The Lord is risen and is seated at the right hand of God, alleluia.

\psalmheading{Psalm 110:1-5,7}

\begin{verse}
The Lord’s revelation to my Master: † \\
“Sit on my right: * \\
your foes I will put beneath your feet.” \\

The Lord will wield from Zion † \\
your scepter of power: *\\
rule in the midst of all your foes. \\

A prince from the day of your birth † \\
on the holy mountains; * \\
from the womb before the dawn I begot you. \\

The Lord has sworn an oath he will not change. † \\
“You are a priest for ever, * \\
a priest like Melchizedek of old.” \\

The Master standing at your right hand * \\
will shatter kings in the day of his great wrath. \\

He shall drink from the stream by the wayside * \\
and therefore he shall lift up his head. \\

Glory to the Father, and to the Son, * \\
and to the Holy Spirit: \\
as it was in the beginning, is now, * \\
and will be for ever. Amen. \\
\end{verse}
\end{document}
