\documentclass[letterpaper,14pt]{extarticle}
\usepackage[fontsize=19pt]{scrextend}
\usepackage[left=0.7in,right=0.3in,top=0.1in,bottom=0.5in]{geometry}
%\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

%\setpdftargetpages

\begin{document}
\hourheading{Memorial of St. Charles Lwanga and Companions}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen.}

%\prayerheading{PSALMODY}
\psalmheading{Psalm 92}
\antiphon{Leader 1}{We do well to sing to your name, Most High, and proclaim your mercy at daybreak.}
\begin{verse}
\side{Leader 1} It is good to give thanks to the Lord,  \\*
\side{Side 1} to make music to your name, O Most High, \\*
to proclaim your love in the morning  \\*
and your truth in the watches of the night, \\*
on the ten-stringed lyre and the lute,  \\*
with the murmuring sound of the harp.

\side{Side 2} Your deeds, O Lord, have made me glad;  \\*
for the work of your hands I shout with joy. \\*
O Lord, how great are your works!  \\*
How deep are your designs! \\*
The foolish man cannot know this  \\*
and the fool cannot understand.

\side{Side 1} Though the wicked spring up like grass  \\*
and all who do evil thrive: \\*
they are doomed to be eternally destroyed.  \\*
But you, Lord, are eternally on high. \\*
See how your enemies perish;  \\*
all doers of evil are scattered.

\side{Side 2} To me you give the wild-ox's strength;  \\*
you anoint me with the purest oil. \\*
My eyes looked in triumph on my foes;  \\*
my ears heard gladly of their fall. \\*
The just will flourish like the palm-tree  \\*
and grow like a Lebanon cedar.

\side{Side 1} Planted in the house of the Lord,  \\*
they will flourish in the courts of our God, \\*
still bearing fruit when they are old,  \\*
still full of sap, still green, \\*
to proclaim that the Lord is just.  \\*
In him, my rock, there is no wrong \\*

\side{Side 2} Glory to the Father, and to the Son,  \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now,  \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{We do well to sing to your name, Most High, and proclaim your mercy at daybreak.}

\psalmheading{Ezekiel 36:24-28}
\antiphon{Leader 2}{I will create a new heart in you, and breathe into you a new spirit.}
\begin{verse}
\side{Leader 2} I will take you away from among the nations, \\*
\side{Side 2} gather you from all the foreign lands, \\*
and bring you back to your own land.

\side{Side 1} I will sprinkle clean water upon you \\*
to cleanse you from all your impurities, \\*
and from all your idols I will cleanse you.

\side{Side 2} I will give you a new heart \\*
and place a new spirit within you, \\*
taking from your bodies your stony hearts \\*
and giving you natural hearts.

\side{Side 1} I will put my spirit within you \\*
and make you live by my statutes, \\*
careful to observe my decrees.

\side{Side 2} You shall live in the land I gave your fathers; \\*
you shall be my people, \\*
and I will be your God.

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{On the lips of children and infants you have found perfect praise.}

\psalmheading{Psalm 8}
\antiphon{Leader 1}{Clothe yourself in everlasting glory, and you will see the splendor of God.}
%\setlength{\stanzaskip}{0.25\baselineskip}
%\vspace{-1.5\baselineskip}
\begin{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\side{Leader 1} How great is your name, O Lord our God, \\*
\side{Side 1} through all the earth!

\side{Side 2} Your majesty is praised above the heavens; \\*
on the lips of children and of babes \\*
you have found praise to foil your enemy, \\*
to silence the foe and the rebel.

\side{Side 1} When I see the heavens, the work of your hands, \\*
the moon and the stars which you arranged, \\*
what is man that you should keep him in mind, \\*
mortal man that you care for him?

\side{Side 2} Yet you have made him little less than a god; \\*
with glory and honor you crowned him, \\*
gave him power over the works of your hands, \\*
put all things under his feet.

\side{Side 1} All of them, sheep and cattle, \\*
yes, even the savage beasts, \\*
birds of the air, and fish \\*
that make their way through the waters.

\side{Side 2} How great is your name, O Lord our God \\*
through all the earth!

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{On the lips of children and infants you have found perfect praise.}


\psalmheading{\textbf{READING}\\2 Cor 1:3,5}
\rednote{Reader:} Praised be God, the Father of our Lord Jesus Christ, the Father of mercies, and the God of all consolation! He comforts us in all our afflictions and thus enables us to comfort those who are in trouble, with the same consolation we have received from him. As we have shared much in the suffering of Christ, so through Christ do we share abundantly in his consolation.
%\newpage
\prayerheading{RESPONSORY}
\begin{verse}
\side{Reader} The just are the friends of God.
They live with him for ever. \\
\side{All} The just are the friends of God.
They live with him for ever.

\side{Reader} God himself is their reward. \\
\side{All} They live with him for ever.

\side{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
\side{All} The just are the friends of God.
They live with him for ever.
\end{verse}

\psalmheading{\textbf{Reflection}}
\psalmheading{\textbf{CANTICLE OF ZECHARIAH}\\ Luke 1:68-79}
\rednote{All stand}
\antiphon{Leader}{Blessed are those who suffer persecution for the sake of justice; the kingdom of heaven is theirs.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} Blessed \rednote{+} be the Lord, the God of Israel; \\*
he has come to his people and set them free.

He has raised up for us a mighty savior, \\*
born of the house of his servant David.

Through his holy prophets he promised of old \\*
  that he would save us from our enemies, \\*
  from the hands of all who hate us.

He promised to show mercy to our fathers \\*
and to remember his holy covenant.

This was the oath he swore to our father Abraham: \\*
to set us free from the hands of our enemies, \\*
free to worship him without fear, \\*
holy and righteous in his sight \\*
   all the days of our life.

You, my child, shall be called the prophet of the Most High; \\*
for you will go before the Lord to prepare his way, \\*
to give his people knowledge of salvation \\*
by the forgiveness of their sins.

In the tender compassion of our God \\*
the dawn from on high shall break upon us, \\*
to shine on those who dwell in darkness and the shadow of death, \\*
and to guide our feet into the way of peace.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{Blessed are those who suffer persecution for the sake of justice; the kingdom of heaven is theirs.}

\prayerheading{INTERCESSIONS}
\intercession{Our Savior’s faithfulness is mirrored in the fidelity of his witnesses who shed their blood for the Word of God. Let us praise him in remembrance of them:}
{\textit{You redeemed us by your blood.}}

\intercession{Your martyrs freely embraced death in bearing witness for the faith,}
{give us the true freedom of the Spirit, O Lord.}

\intercession{Your martyrs professed their faith by shedding their blood,}
{give us a faith, O Lord, that is constant and pure.}

\intercession{Your martyrs followed in your footsteps by carrying the cross,}
{help us to endure courageously the misfortunes of life.}

\intercession{Your martyrs washed their garments in the blood of the Lamb,}
{help us to avoid the weaknesses of the flesh and worldly allurements.}

\prayerheading{THE LORD'S PRAYER}
\antiphon{Leader}{Gathering our prayer and praises into one, let us offer the prayer Christ himself taught us:}
	
\begin{verse}
	\side{All} Our Father, who art in heaven,\\ %[$\cdots$] \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\psalmheading{CONCLUSION}

\sidestar{President}\\*

O God, who have made the blood of Martyrs \\*
the seed of Christians, \\*
mercifully grant that the field which is your Church, \\*
watered by the blood \\*
shed by Saints Charles Lwanga and his companions, \\*
may be fertile and always yield you an abundant harvest. \\*
Through our Lord Jesus Christ, your Son,\\*
who lives and reigns with you in the unity of the Holy Spirit,\\*
God, for ever and ever.\\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{President}
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.

\sidestar{President}
May the souls of the faithful departed,  \\*
through the mercy of God, rest in peace. \\*
\sidestar{All} Amen.

\end{document}
