\documentclass[letterpaper,14pt]{extarticle}
\usepackage[fontsize=20pt]{scrextend}
\usepackage[left=0.49in,right=0.2in,top=0.1in,bottom=0.5in]{geometry}
%\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}:}}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

%\setpdftargetpages

\begin{document}
\hourheading{Saturday of the Third Week of Lent}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance.}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen.}

\prayerheading{HYMN}

\rednote{Be Seated}
%\prayerheading{PSALMODY}
\psalmheading{Psalm 119:145-152 XIX (Koph)}
\antiphon{Leader 1}{Lord, you are near to us, and all your ways are true.}
\begin{verse}
\side{Leader 1} I call with all my heart; Lord, hear me, \\*
\side{Side 1} I will keep your commands. \\*
I call upon you, save me \\*
and I will do your will.

\side{Side 2} I rise before dawn and cry for help, \\*
I hope in your word.\\*
My eyes watch through the night \\*
to ponder your promise.

\side{Side 1} In your love hear my voice, O Lord; \\*
give me life by your decrees.\\*
Those who harm me unjustly draw near: \\*
they are far from your law.

\side{Side 2} But you, O Lord, are close:\\* 
your commands are truth.\\*
Long have I known that your will \\*
is established for ever.

\side{Side 1} Glory to the Father, and to the Son,  \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now,  \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{Lord, you are near to us, and all your ways are true.}


\psalmheading{Canticle: Wisdom 9:1-6, 9-11}
\antiphon{Leader 2}{Wisdom of God, be with me, always at work in me.}
\begin{verse}
\side{Leader 2} God of my fathers, Lord of mercy, \\*
\side{Side 2} you who have made all things by your word \\*
and in your wisdom have established man \\*
to rule the creatures produced by you, \\*
to govern the world in holiness and justice, \\*
and to render judgment in integrity of heart:

\side{Side 1} Give me Wisdom, the attendant at your throne, \\*
and reject me not from among your children; \\*
for I am your servant, the son of your handmaid, \\*
a man weak and short-lived \\*
and lacking in comprehension of judgment and of laws.

\side{Side 2} Indeed, though one be perfect among the sons of men, \\*
if Wisdom, who comes from you, be not with him, \\*
he shall be held in no esteem.

\side{Side 1} Now with you is Wisdom, who knows your works\\*
and was present when you made the world;\\*
who understands what is pleasing in your eyes\\*
and what is conformable with your commands.

\side{Side 2} Send her forth from your holy heavens \\*
and from your glorious throne dispatch her \\*
that she may be with me and work with me, \\*
that I may know what is your pleasure.

\side{Side 1} For she knows and understands all things, \\*
and will guide me discreetly in my affairs \\*
and safeguard me by her glory.

\side{Side 2} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 1} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{Wisdom of God, be with me, always at work in me.}

\psalmheading{Psalm 117}
\antiphon{Leader 1}{The Lord remains faithful to his promise for ever.}
%\setlength{\stanzaskip}{0.25\baselineskip}
%\vspace{-1.5\baselineskip}
\begin{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\side{Leader 1} O praise the Lord, all you nations, \\*
\side{Side 1} acclaim him, all you peoples!

\side{Side 2} Strong is his love for us; \\*
he is faithful for ever.

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{The Lord remains faithful to his promise for ever.}


\psalmheading{\textbf{READING}\\Isaiah 1:16-18}
\begin{verse}
\side{Reader} 
Wash yourselves clean! \\*
Put away your misdeeds from before my eyes; \\*
cease doing evil; learn to do good. \\*
Make justice your aim; redress the wronged, \\*
hear the orphan's plea, defend the widow. \\*
Come now, let us set things right, \\*
says the Lord: \\*
Though your sins be like scarlet, \\*
they may become white as snow; \\*
Though they be crimson red, \\*
they may become white as wool.
\end{verse}

%\newpage
\prayerheading{RESPONSORY}
\begin{verse}
\side{Reader} God himself will set me free, from the hunter's snare. \\
\side{All} God himself will set me free, from the hunter's snare.

\side{Reader} From those who would trap me with lying words\\
\side{All} and from the hunter's snare.

\side{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
\side{All} God himself will set me free, from the hunter's snare.
\end{verse}
%\psalmheading{\textbf{Reflection}}
\psalmheading{\textbf{CANTICLE OF ZECHARIAH}\\ Luke 1:68-79}
\rednote{All stand}
\antiphon{Leader}{The tax collector stood far away and would not even raise his eyes to heaven. He struck his breast and prayed: God, have mercy on me, a sinner.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} Blessed \rednote{+} be the Lord, the God of Israel; \\*
he has come to his people and set them free.

He has raised up for us a mighty savior, \\*
born of the house of his servant David.

Through his holy prophets he promised of old \\*
  that he would save us from our enemies, \\*
  from the hands of all who hate us.

He promised to show mercy to our fathers \\*
and to remember his holy covenant.

This was the oath he swore to our father Abraham: \\*
to set us free from the hands of our enemies, \\*
free to worship him without fear, \\*
holy and righteous in his sight \\*
   all the days of our life.

You, my child, shall be called the prophet of the Most High; \\*
for you will go before the Lord to prepare his way, \\*
to give his people knowledge of salvation \\*
by the forgiveness of their sins.

In the tender compassion of our God \\*
the dawn from on high shall break upon us, \\*
to shine on those who dwell in darkness and the shadow of death, \\*
and to guide our feet into the way of peace.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{The tax collector stood far away and would not even raise his eyes to heaven. He struck his breast and prayed: God, have mercy on me, a sinner.}
\prayerheading{INTERCESSIONS}
\intercession{To make us his new creation, Christ the Lord gave us the waters of rebirth and spread the table of his body and his word. Let us call upon him and say:}
{\textit{Lord, renew us in your grace.}}

\intercession{Jesus, meek and humble of heart, clothe us with compassion, kindness and humility,}
{make us want to be patient with everyone.}

\intercession{Teach us to be true neighbors to all in trouble and distress,}
{and so imitate you, the Good Samaritan.}

\intercession{May the Blessed Virgin, your Mother, pray for all those vowed to a life of virginity,}
{that they may deepen their dedication to you and to the Church.}

\intercession{Grant us the gift of your mercy,}
{forgive our sins and remit their punishment.}

\prayerheading{THE LORD'S PRAYER}
%\antiphon{Leader}{Remember us, Lord, when you come to your kingdom and teach us how to pray:}
	
\begin{verse}
	\side{All} Our Father, who art in heaven,\\ %[$\cdots$] \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\psalmheading{CONCLUSION}

\begin{verse}
\side{Pastor} Rejoicing in this annual celebration \\*
of our Lenten observance, \\*
we pray, O Lord, \\*
that, with our hearts set on the paschal mysteries, \\*
we may be gladdened by their full effects. \\*
Through our Lord Jesus Christ, your Son,\\*
who lives and reigns with you in the unity of the Holy Spirit,\\*
God, for ever and ever.\\*
\side{All} Amen.
\end{verse}
\prayerheading{DISMISSAL}

\begin{verse}
\side{Pastor} The Lord be with you. \\*
\side{All} And with your spirit. \\*
\side{Pastor} May almighty God bless you, \\*
the Father, and the Son and the Holy Spirit. \\*
\side{All} Amen. \\*
\side{Pastor} Go in peace. \\*
\side{All} Thanks be to God. \\*
\side{Pastor}
May the souls of the faithful departed,  \\*
through the mercy of God, rest in peace. \\*
\side{All} Amen.
\end{verse}

\end{document}
