\documentclass[letterpaper,14pt]{extarticle}
\usepackage[fontsize=19pt]{scrextend}
\usepackage[left=0.7in,right=0.3in,top=0.1in,bottom=0.5in]{geometry}
%\usepackage[print]{booklet}
\usepackage{xcolor}
\usepackage{liturg}
\usepackage{alltt}
\usepackage{verse}
%\usepackage{calc}
%\usepackage{scrextend}

\newcommand{\side}[1]{\flagverse{\textcolor{red}{\textit{#1}}:}}
\newcommand{\sidestar}[1]{\textcolor{red}{\textit{#1}:}}
\newcommand{\rednote}[1]{\textcolor{red}{#1}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\vleftskip}{8pt}
\setlength{\leftmargini}{4.5em}
\newlength{\oldindent}


\newcommand{\antiphon}[2]{
	\setlength{\oldindent}{\vindent}
	\setlength{\vindent}{0em}
	\begin{verse}
	\side{#1} \textbf{#2}
	\end{verse}
	\setlength{\vindent}{\oldindent}
}
\newcommand{\intercession}[2]{
	\begin{tabular}[h]{r p{4.25in}}
		\sidestar{Leader} & #1 \\
		\sidestar{All} & #2
	\end{tabular}}



\newcommand{\psalm}[4][1]{%
\setcounter{side}{#1}
\psalmheading{#2}
\antiphon{Leader #1}{#3}
\begin{verse}
#4
\end{verse}
\antiphon{All}{#3}
}

%\setpdftargetpages

\begin{document}
\hourheading{Thursday of the First Week in Lent}
\prayerheading{INTRODUCTION}
\hspace{\leftmargini}\rednote{(Make sign of cross)}\\
\intercession{God, \rednote{+} come to my assistance}
{Lord, make haste to help me.}\\
\intercession{Glory to the Father, and to the Son and to the Holy Spirit:}
{as it was in the beginning, is now, and will be for ever. Amen.}

%\prayerheading{PSALMODY}
\psalmheading{Psalm 30}
\antiphon{Leader 1}{I cried to you, Lord, and you healed me; I will praise you for ever.}
\begin{verse}
\side{Leader 1} I will praise you, Lord, you have rescued me \\*
\side{Side 1} and have not let my enemies rejoice over me. 

\side{Side 2} O Lord, I cried to you for help \\*
and you, my God, have healed me. \\*
O Lord, you have raised my soul from the dead, \\*
restored me to life from those who sink into the grave.

\side{Side 1} Sing psalms to the Lord, you who love him, \\*
give thanks to his holy name. \\*
His anger lasts but a moment; his favor through life. \\*
At night there are tears, but joy comes with dawn.

\side{Side 2} I said to myself in my good fortune: \\*
“Nothing will ever disturb me.” \\*
Your favor had set me on a mountain fastness, \\*
then you hid your face and I was put to confusion.

\side{Side 1} To you, Lord, I cried, \\*
to my God I made appeal: \\*
“What profit would my death be, my going to the grave? \\*
Can dust give you praise or proclaim your truth?”

\side{Side 2} The Lord listened and had pity. \\*
The Lord came to my help. \\*
For me you have changed my mourning into dancing, \\*
you removed my sackcloth and clothed me with joy. \\*
So my soul sings psalms to you unceasingly. \\*
O Lord my God, I will thank you for ever.

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{Leader 1}{I cried to you, Lord, and you healed me; I will praise you for ever.}

\psalmheading{Psalm 32}
\antiphon{Leader 2}{The one who is sinless in the eyes of God is blessed indeed.}
\begin{verse}
\side{Leader 2} Happy the man whose offense is forgiven, \\*
\side{Side 2} whose sin is remitted. \\*
O happy the man to whom the Lord \\*
imputes no guilt, \\*
in whose spirit is no guile.

\side{Side 1} I kept it secret and my frame was wasted. \\*
I groaned all the day long \\*
for night and day your hand \\*
was heavy upon me. \\*
Indeed, my strength was dried up \\*
as by the summer’s heat.

\side{Side 2} But now I have acknowledged my sins; \\*
my guilt I did not hide. \\*
I said: “I will confess \\*
my offense to the Lord.” \\*
And you, Lord, have forgiven \\*
the guilt of my sin.

\side{Side 1} So let every good man pray to you \\*
in the time of need. \\*
The floods of water may reach high \\*
but him they shall not reach. \\*
You are my hiding place, O Lord; \\*
you save me from distress. \\*
You surround me with cries of deliverance.

\side{Side 2} I will instruct you and teach you \\*
the way you should go; \\*
I will give you counsel \\*
with my eye upon you.

\side{Side 1} Be not like horse and mule, unintelligent, \\*
needing bridle and bit, \\*
else they will not approach you. \\*
Many sorrows has the wicked \\*
but he who trusts in the Lord, \\*
loving mercy surrounds him.

\side{Side 2} Rejoice, rejoice in the Lord, \\*
exult, you just! \\*
O come, ring out your joy, \\*
all you upright of heart.

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2}as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
\antiphon{All}{The one who is sinless in the eyes of God is blessed indeed.}

\psalmheading{Revelation 11:17-18; 12:10b-12a}
\antiphon{Leader 1}{The Father has given Christ all power, honor and kingship; all people will obey him.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\vspace{-1.5\baselineskip}
\begin{verse}
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\side{Leader 1} We praise you, the Lord God Almighty, \\*
\side{Side 1} who is and who was. \\*
You have assumed your great power, \\*
you have begun your reign.

\side{Side 2} The nations have raged in anger, \\*
but then came your day of wrath \\*
and the moment to judge the dead: \\*
the time to reward your servants the prophets \\*
and the holy ones who revere you, \\*
the great and the small alike.

\side{Side 1} Now have salvation and power come, \\*
the reign of our God and the authority \\*
of his Anointed One. \\*
For the accuser of our brothers is cast out, \\*
who night and day accused them before God.

\side{Side 2} They defeated him by the blood of the Lamb \\*
and by the word of their testimony; \\*
love for life did not deter them from death. \\*
So rejoice, you heavens, \\*
and you that dwell therein!

\side{Side 1} Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
\side{Side 2} as it was in the beginning, is now, \\*
and will be for ever. Amen.
\antiphon{All}{The Father has given Christ all power, honor and kingship; all people will obey him.}


\psalmheading{\textbf{READING}\\James 4:7-8, 10}
\begin{verse}
\side{Reader}Submit to God; resist the devil and he will take flight. Draw close to God, and he will draw close to you. Cleanse your hands, you sinners; purify your hearts, you backsliders. Be humbled in the sight of the Lord and he will raise you on high.
\end{verse}
%\newpage
\prayerheading{RESPONSORY}
\begin{verse}
\side{Reader} To you, O Lord, I make my prayer for mercy. \\
\side{All} To you, O Lord, I make my prayer for mercy.

\side{Reader} Heal my soul, for I have sinned against you. \\
\side{All} I make my prayer for mercy.

\side{Reader} Glory to the Father, and to the Son, and to the Holy Spirit. \\
\side{All} To you, O Lord, I make my prayer for mercy.
\end{verse}

\psalmheading{\textbf{CANTICLE OF MARY}\\ Luke 1:49-55}
\rednote{All stand}
\antiphon{Leader}{Ask and you shall receive; seek and you shall find; knock and the door will be opened to you.}
%\setlength{\stanzaskip}{0.25\baselineskip}
\begin{verse}
\rednote{(Make sign of cross)}\\
\side{All} My \rednote{+} soul proclaims the greatness of the Lord, \\*
my spirit rejoices in God my Savior \\*
for he has looked with favor on his lowly servant.

From this day all generations will call me blessed: \\*
the Almighty has done great things for me, \\*
and holy is his Name.

He has mercy on those who fear him \\*
in every generation.

He has shown the strength of his arm, \\*
he has scattered the proud in their conceit.

He has cast down the mighty from their thrones, \\*
and has lifted up the lowly.

He has filled the hungry with good things, \\*
and the rich he has sent away empty.

He has come to the help of his servant Israel \\*
for he has remembered his promise of mercy, \\*
the promise he made to our fathers, \\*
to Abraham and his children for ever.

Glory to the Father, and to the Son, \\*
and to the Holy Spirit: \\*
as it was in the beginning, is now, \\*
and will be for ever. Amen.
\end{verse}
%\setlength{\stanzaskip}{0.75\baselineskip}
\antiphon{All}{Ask and you shall receive; seek and you shall find; knock and the door will be opened to you.}

\prayerheading{INTERCESSIONS}
\intercession{Christ the Lord gave us a new commandment, of love for each other. Let us pray to him:}
{\textit{Lord, build up your people in love.}}

\intercession{Good Master, teach us to love you in our neighbor,}
{and in serving them to serve you.}

\intercession{On the cross you asked pardon for your executioners,}
{give us strength to love our enemies and pray for those who persecute us.}

\intercession{Through the mystery of your body and blood, deepen our love, our perseverance and our trust,}
{strengthen the weak, console the sorrowful, and give hope to the dying.}

\intercession{Light of the world, you gave light to the man born blind when he had washed in the pool of Siloam,}
{enlighten catechumens through the water of baptism and the word of life.}

\intercession{Give to the dead the perfect joy of your eternal love,}
{and number us also among your chosen ones.}

\prayerheading{THE LORD'S PRAYER}
\antiphon{Leader}{Remember us, Lord, when you come to your kingdom and teach us how to pray:}
	
\begin{verse}
	\side{All} Our Father, who art in heaven,\\ %[$\cdots$] \\
hallowed be thy name; \\
thy kingdom come; \\
thy will be done on earth \\
as it is in heaven. \\
Give us this day our daily bread; \\
and forgive us our trespasses \\
as we forgive those who trespass against us; \\
and lead us not into temptation, \\
but deliver us from evil.
\end{verse}

\psalmheading{CONCLUSION}

\sidestar{Leader}\\*
Bestow on us, we pray, O Lord, \\*
a spirit always pondering on what is right\\*
and of hastening to carry it out,\\*
and, since without you we cannot exist,\\*
may we be enabled to live according to your will.\\*
Through our Lord Jesus Christ, your Son,\\*
who lives and reigns with you in the unity of the Holy Spirit,\\*
God, for ever and ever.\\*
\sidestar{All} Amen.

\prayerheading{DISMISSAL}

\sidestar{Leader}\\*
May the Lord \rednote{+} bless us, \\*
protect us from all evil \\*
and bring us to everlasting life. \\*
\sidestar{All} Amen.
\end{document}
