\side{Leader 2}Give ear, O heavens, while I speak; \\*
\side{Side 2}let the earth hearken to the words of my mouth!\\*
May my instruction soak in like the rain, \\*
and my discourse permeate like the dew,\\*
like a downpour upon the grass, \\*
like a shower upon the crops:

\side{Side 1}For I will sing the Lord's renown. \\*
Oh, proclaim the greatness of our God!\\*
The Rock—how faultless are his deeds, \\*
how right all his ways!\\*
A faithful God, without deceit, \\*
how just and upright he is!

\side{Side 2}Yet basely has he been treated by his degenerate children, \\*
a perverse and crooked race!\\*
Is the Lord to be thus repaid by you, \\*
O stupid and foolish people?\\*
Is he not your father who created you? \\*
Has he not made you and established you?

\side{Side 1}Think back on the days of old, \\*
reflect on the years of age upon age.\\*
Ask your father and he will inform you, \\*
ask your elders and they will tell you:

\side{Side 2}When the Most High assigned the nations their heritage, \\*
when he parceled out the descendants of Adam,\\*
he set up the boundaries of the peoples \\*
after the number of the sons of God;\\*
while the Lord's own portion was Jacob, \\*
his hereditary share was Israel.

\side{Side 1}He found them in a wilderness, \\*
a wasteland of howling desert.\\*
He shielded them and cared for them, \\*
guarding them as the apple of his eye.

\side{Side 2}As an eagle incites its nestlings forth \\*
by hovering over its brood,\\*
so he spread his wings to receive them \\*
and bore them up on his pinions.\\*
The Lord alone was their leader, \\*
no strange god was with him.

\side{Side 1}Glory to the Father, and to the Son,\\*
and to the Holy Spirit:\\*
\side{Side 2}as it was in the beginning, is now,\\*
and will be for ever. Amen.